---
title: "Assignment week 14"
author: Ditte Danielsen 
output: html_document
---

# Interactive map  

## Task 1: Create a Danish equivalent of AUSmap with esri layers, but call it DANmap

### Libraries

```{r}
library(tidyverse)
library(googlesheets4)
library(leaflet)
```

###Read in a Google sheet
places2 <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps2McZx1cTVWSzI/edit#gid=124710918",
                     col_types = "cccnncnc")
```{r}
places <- read.csv("CapturingCoordinates - DM2023.csv")

glimpse(places)
```

### load the coordinates in the map and check: are any points missing? Why?
```{r}
DANmap <- leaflet() %>% 
  addTiles() %>%
  addProviderTiles("Stadia.OSMBright") %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description)
```

##Task 2: Read in the googlesheet data you and your colleagues 
###Populated with data into the DANmap object you created in Task 1.


```{r}
DANmap
```

## Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"
```{r}
DANmap_clusters <- leaflet() %>% 
  addTiles() %>%
  addProviderTiles("Stadia.OSMBright") %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description,
             clusterOptions = markerClusterOptions()) 

DANmap_clusters
```
## Task 4: Look at the map and consider what it is good for and what not.
It is a good map for quickly seeing, in what areas of the country there are things to see and do, according to our classmates. A downside to the clustering-tool, it doesnt show precise locations until you zoom in on the map. 

## Task 5: Find out how to display notes and classifications in the map.
```{r}
DANmap_popups <- leaflet() %>% 
  addTiles() %>%
  addProviderTiles("Stadia.OSMBright") %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup=paste(
               "By:", places$X, "<br>",
               "Type:", places$Type, "<br>",
               "Descriprion:",places$Description),
             clusterOptions = markerClusterOptions()) 
DANmap_popups
```



